\thispagestyle{empty}

\COPYRIGHT

\textbf{License}

Licensed under the Apache License, Version 2.0 (the "License"); you may not use this file except in compliance with the License. You may obtain a copy of the License at:

\url{http://www.apache.org/licenses/LICENSE-2.0}

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied. See the License for the specific language governing permissions and limitations under the License.

\textbf{Trademark}

Anaconda is a registered trademark of Anaconda, Inc. C\#, .NET, PowerShell, and Windows are registered trademarks of the Microsoft Corporation. Java is a registered trademark of the Oracle Corporation. Linux is a registered trademark of Linus Torvalds. Python and the Python logo are a registered trademarks of the Python Software Foundation. Use of the Python logo does not imply endorsement by the Python Software Foundation.

\textbf{Authors}

% Defined in utilities/variables.txt
\AUTHORS

\textbf{Abstract}

Python is an interpreted, general purpose programming language that excels in a variety of roles. Because of its flexibility and the speed at which it can be used to complete projects, Python is increasingly being used within the financial services sector. Python is unlike more traditional enterprise languages, such as COBOL, Java, and C\#; consequently it has a unique risk profile that benefits from individualized treatment. The purpose of this document is to provide a model set of rules for the governance and use of the Python language for data analysis and processing in the financial services context.
